### 2018-01-14 Project log/multiple_outcomes_project_log.Rmd
Simplify stitching

@@

@@

\item{ Bootstrap from original sample with 100 independent std. normal; reject using z-test that’s only a function of mean $\Rightarrow$ \textbf{DOESN'T WORK} 
  \begin{itemize}
    \item	The bootstrapped distribution of the absolute differences is too variable compared to true distribution
    \item	Hence rejects only 1.8\% of time
  \end{itemize}
}

>>>>

2018-1-15
Mysteries: 
* Understand why FCR resampling doesn't work (these resamples reject more often than the original data). I found that prob of rejection even when there is only 1 covariate is too high. In my simple script, try resampling residuals and re-attaching them to fitted values. Does that work?
* Is it theoretically valid to use the weird CI for excess hits using the observed hits and the CI under the null?

@@

\subsection{2017-8-1 (generate under $H_0$ and $H_A$)}

\begin{itemize}
\item FCR resampling doesn't seem to work because even when data generated under the null, the resamples have more than the expected number of rejections
\item Not due to lower truncation because using alpha = 0.5 doesn't help
\item Seems like correlations are preserved in individual resamples?
\item But I think the correlations are more variable, even if their mean is still 0, because sometimes we draw samples that have a lot of repetition
\end{itemize}

@@

\item{ Bootstrap from original sample with 100 independent std. normal; reject using z-test that’s only a function of mean because SD is treated as known $\Rightarrow$ \textbf{DOESN'T WORK} 
  \begin{itemize}
    \item	The bootstrapped distribution of the absolute differences is too variable compared to true distribution
    \item	Hence rejects only 1.8\% of time
  \end{itemize}
}
